A Bayesian ranking statistic to find high-mass black holes in LIGO--Virgo data

### 2021-03-29 main.tex

Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range. \rory{\sout{However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s~\cite{}. Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers. This tight constraint makes hierarchical mergers a challenging scenario.}

@@

\rory{\sout{It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~). However, this dynamic measurement method is challenging to utilise for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}. Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g. the candidate at the centre of the globular cluster 47 Tucanae~\cite{kiziltan 2017}, can also be attributed to simpler models without a central  intermediate-mass black hole~\cite{freire 2017}. }}

\rory{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al. 2000}, they cannot accurately estimate the intermediate-masses. The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an central intermediate-mass black hole~\cite{J. E. Greene and L. C. Ho The Mass Function of Active Black Holes in the Local Universe, E. C. Moran, K. Shahinyan, H. R. Sugarman, D. O. Vélez and M. Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}. Table 2 of~\citet{mercuza} displays a list of intermediate-mass candidates found with these relations. }}

\rory{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}. Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully. However, this method fails to measure the systematic uncertainties on the lower-end of the intermediate-mass spectrum~\cite{}. Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of intermediate-mass candidates found with reverberation mapping~\cite{}. }}

The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g. HLX-X1)~\cite{}. \rory{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}. However, some argue that some stellar mass black holes may exceed the Eddington limit~\cite{}, and others argue that the X-ray emission might be from a collimated jet leading to an inaccurate mass calculation~\cite{}.}}

\Finally, \rory{\sout{another channel to measure black hole masses is by identifying}} Gravitational waves from compact binaries coalesces (CBCs) \rory{are clean channels to measure BH masses} \rory{\sout{ inferring their source parameters~\cite{}.}} Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$. As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_T^-1$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$. Hence, ground based gravitational wave detectors ($\sim 10 - 1000\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 500 \msun$, while space-based detectors ($\sim 0.1 - 10\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$.

>>>>

Hierarchical mergers in active galactic nuclei migration-traps, globular and stellar clusters may be a feasible light-seed method for black holes to accumulate mass and reach the intermediate-mass range. \rs{\sout{However, when black holes merge, they can receive recoil-kicks up to $\sim$2,500 km/s~\cite{}. Hence, the merger remnants require their recoil kick to be less than its environment's escape velocity to undergo successive mergers. This tight constraint makes hierarchical mergers a challenging scenario.}

@@

\rs{\sout{It is possible to measure the mass of nearby supermassive black holes by directly observing the dynamic motion of stars nearby the supermassive black hole (such as Sgr A$^*$~). However, this dynamic measurement method is challenging to utilise for  intermediate-mass black holes as their sphere of influence is too small to resolve motions~\cite{}. Additionally, dynamic-measurements that have alluded to  intermediate-mass candidates, e.g. the candidate at the centre of the globular cluster 47 Tucanae~\cite{kiziltan 2017}, can also be attributed to simpler models without a central  intermediate-mass black hole~\cite{freire 2017}. }}

\rs{\sout{In a similar vein, although the M-$\sigma$ and M-L relations (relations between the spheroidal bulge of a galaxy's velocity dispersion $\sigma$,  luminosity L, and its central black hole's mass M) can estimate the mass of supermassive black holes~\cite{Ferrarese & Merritt 2000 and Gebhardt et al. 2000}, they cannot accurately estimate the intermediate-masses. The M-$\sigma$ and M-L relations are not calibrated for low-mass galaxies that might host an central intermediate-mass black hole~\cite{J. E. Greene and L. C. Ho The Mass Function of Active Black Holes in the Local Universe, E. C. Moran, K. Shahinyan, H. R. Sugarman, D. O. Vélez and M. Eracleous Black Holes At the Centers of Nearby Dwarf Galaxies}. Table 2 of~\citet{mercuza} displays a list of intermediate-mass candidates found with these relations. }}

\rs{\sout{Another method to estimate large black hole masses is with reverberation mapping, which estimates black hole virial masses by studying their nearby gasses' velocities~\cite{reverberation mapping}. Reverberation mapping has shown to estimate both supermassive black hole and intermediate-mass black hole virial masses successfully. However, this method fails to measure the systematic uncertainties on the lower-end of the intermediate-mass spectrum~\cite{}. Additionally, cloud-variability and the possibility of anisotropic emission deride the credibility of intermediate-mass candidates found with reverberation mapping~\cite{}. }}

The most promising intermediate-mass candidates found with electromagnetic-spectra are Ultra-Luminous X-ray sources with luminosities $> 10^{39} \text{erg s}^{-1}$ (e.g. HLX-X1)~\cite{}. \rs{\sout{While stellar mass black holes are too small to generate such luminosities with Eddington accretion, intermediate mass black holes can accrete at rates large enough to account for the high luminosities~\cite{}. However, some argue that some stellar mass black holes may exceed the Eddington limit~\cite{}, and others argue that the X-ray emission might be from a collimated jet leading to an inaccurate mass calculation~\cite{}.}}

\Finally, \rs{\sout{another channel to measure black hole masses is by identifying}} Gravitational waves from compact binaries coalesces (CBCs) \rs{are clean channels to measure BH masses} \rs{\sout{ inferring their source parameters~\cite{}.}} Mergers involving either a binary system with at least one intermediate-mass component, or a system whose merger results in an intermediate-mass remnant will have large initial total masses $\text{M}_{T}$. As a binary's $\text{M}_{T}$ is associated with its merger frequency, $f\sim \text{M}_T^-1$, systems with large $\text{M}_{T}$ have very low merger frequencies $f < 100\ \text{Hz}$. Hence, ground based gravitational wave detectors ($\sim 10 - 1000\ \text{Hz}$) are sensitive to the last milliseconds of merging systems with $100 \msun < \text{M}_{T} < 500 \msun$, while space-based detectors ($\sim 0.1 - 10\ \text{Hz}$) can study the full signals of merging systems with $10^4 \msun < \text{M}_{T} < 10^7 \msun$.
